The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-27 paper/paper.Rmd
Modify flowchart.
Fix error in flowchart's caption.
Edit flowchart's caption.

```{r flow-chart, fig.cap="The stages of data cleaning from the raw data to get three datasets contained yowie. n individuals means the number of respondents included in each stage, while n observations means the number of rows in the data. The color represented the stage of data cleaning in statistical value chain (van der Loo \\& de Jonge, 2018). Pink, blue, and green represents the raw, input, and valid data, respectively.", out.width="85%"}
```

>>>>

```{r flow-chart, fig.cap="The stages of data cleaning from the raw data to get three datasets contained yowie. \\# of individuals means the number of respondents included in each stage, while \\# of observations means the number of rows in the data. The color represents the stage of data cleaning in statistical value chain (van der Loo \\& de Jonge, 2018). Pink, blue, and green represents the raw, input, and valid data, respectively.", out.width="85%"}
```
